Type-Safe Modular Parsing

### 2016-11-30 paper/sections/RelatedWork.tex
Related work: modular datatypes.

\paragraph*{Modular Datatypes} Text.

>>>>

\paragraph*{Modular Datatypes} There has been lots of related work on building modular data structures, especially in some functional languages with non-extensible datatypes like Haskell. For instance, the famous DTC paper [] represents modular ASTs using co-products of every two functors, which forms a binary tree structure. It supports extensible datatypes, as well as the operations on them by implementing instances of functors. Later Oliveira et al. presented MRM [] in Haskell, which is similar to DTC but adopts a list of functors in type-level lists instead. As mentioned above, we have conducted our early experiment with MRM for modular datatypes, whereas the complexity of library implementation was comparably high.

In OO languages, however, things get much better with the mechanism of inheritance. Furthermore, Object Algebras [] were proposed as a design pattern for the extensibility of both data variants and operations in a modular type-safe way. The code is concise and expressive using Object Algebras, building a foundation for our new library with various dimensions of extensibility. \haoyuan{To mention: noa and modular semantic actions, and shy use Object Algebras, shy and mrm can override cases.}
